---
title: "**R Course:** <br> Homework 2 <br> *My Cheat Sheet*"
author: "Lingyun Yang"

output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true    
    number_sections: true

---
# Vectors

create a vector: *c()*

## Numeric vectors

```{r}
a <- c(1, 2, 3)
a
```

## Character vectors

```{r}
b <- c('o', 'f', 'h', 'u')
b
```

*cannot include both numbers and characters

```{r}
c("a", 2)
```

## Logical vector

```{r}
d <- c("TRUE", "FALSE")# It can automatically find data which adhere to a set of arguments you specify
x <- runif(n = 10, min = 0, max = 20)
x
x > 5
```

### Logical operators

|Logical operator|Code|Example|
|:-----|:-----|:-----|
|Equal to|==|c(1:5) == 2|
|Not equal to|!=|c(1:5) == 3|
|Less than|<|4 < 5|
|More than|>|3 > 5|
|Less than or equal to|<=|c(1:5) <= 3|
|More than or equal to|>=|c(1:5) >= 2|
|Or|&#124;|x <- c(1:5) ; x > 3 | x < 2|
|Within|%in%|1:10 %in% c(1,3,5,9)|

using *&#124*; take place of |

## Combine multiple vectors

(1

```{r}
g <- c(10, 4)#make a new vector
c(a , g)
```

(2

```{r}
g <- c(10, a, 4)
g
```

## Add name

(1

```{r}
my_vec <- c("a" = 1, "d" = 3, "b" = 2)
my_vec
```

(2

```{r}
my_vec <- c(1, 3, 2)
names(my_vec) <- c("a", "d", "b")
my_vec
```

## Select vector elements

use*[ ]*

(1 By position

```{r}
my_vec[2]#The second element.
```

```{r}
my_vec[-2]#All but the second.
```

```{r}
my_vec[1:3]#Elements one to three.
```

```{r}
my_vec[-(1:2)]#All elements except one to three.
```

```{r}
my_vec[c(2, 3)]#Elements two and three.
```

(2 By value

```{r}
my_vec[my_vec == 2]#Elements which are equal to 2.
```

```{r}
my_vec[my_vec > 0]#All elements more than zero.
```

```{r}
my_vec[my_vec %in% c(1, 2)]#Elements in the set 1, 2.
```

(3 Named Vectors

```{r}
my_vec["d"]#Element with name ‘d'
```

## Checking vector

```{r}
is.numeric(1:5)
```

```{r}
is.character(letters[1:5])
```

```{r}
is.logical(c(TRUE, 1))
```

## Factors

```{r}
##student names
class_names <- c("James", "John", "Mary", "Linda", "Susan", "Mary", "Charles", "John", "James")

##convert the student names to a factor
class_names <- as.factor(class_names)

##look at the factor
class_names

##look at only the levels
levels(class_names)
```

# Functions

## Getting help

use*?*

```{r, eval = FALSE}
?mean()
```

<center>

![Description of
Mean](Screenshot%202021-10-11%20235440.png){width="66%"}

</center>

## Writing function

use *function()*

```{r}
se <- function(x){

   std_er<-sd(x)/sqrt(length(x))

   return(std_er)
}
```

## Useful functions

|Function|Call|
|:-----|:------|
|Create a vector|c()|
|Return the length of a vector|length()|
|Check the names of a vector or add names to a vector|names()|
|Sort a vector by value|sort()|
|Reverse a vector by value|rev()|
|Make a vector into a factor|as.factor()|
|Generate random numbers from a uniform distribution|runif()|
|Add up the values of a vector|sum()|
|Calculate the average of the values of a vector|mean()|
|Round a vector to the nearest ….|round()|
|Square root of the values in a vector|sqrt()|
|Create a function|function()|
|Return the desired object from a function|return()|
|An integer sequence|2:6|
|A complex sequence|seq()|
|Clear R’s memory|rm(list = ls())|
|Random numbers from a uniform distribution|rnorm()|

